\Large{Adversarial Variational Optimization of Non-Differentiable Simulators}

### 2017-06-22 paper.tex
save

\glnote{Implicit generative models.}
\glnote{gan + classifier ABC.}

\glnote{likelihood free inference, density ratio by classification}
\glnote{carl~\citep{cranmer2015approximating}.}

>>>>

As reviewed in \cite{2016arXiv161003483M}, likelihood-free inference is
intimately tied to a class of algorithms that can be framed as density
estimation-by-comparison. In most cases, these algorithms are formulated as an
iterative two-step process where the model distribution is first compared to the
true data distribution and then updated to make it more comparable to the
latter. Closest to our work are inference
algorithms~\citep{Neal:2007zz,gutmann2012noise,goodfellow2014generative,cranmer2015approximating,2016arXiv161110242D}
that rely on a classifier between generated and true data to estimate the
density ratio between the two distributions and make parameter updates.
\glnote{ABC + Classifier ABC.}
\glnote{Explain how this work is different.}
